How to compute the fusion product of MV cycles in type A

### 2021-05-15 draft.tex
questions in fusion section

\section{Introduction}
\label{s:intro}
% 
Throughout this paper (unless indicated otherwise) the base field is $\CC$.

@@

Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.

%Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (\cref{it:polyno-taylor,it:grs-gr} of \cref{ss:relsbtwgrs} preceding), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
% TODO: cf https://tex.stackexchange.com/questions/256849/cleveref-change-behaviour-of-cref-to-use-the-abbreviated-form

These isomorphisms $ \tau_s $ defined above glue together to a projection map
\begin{equation}
\label{eq:mvitau}
    \tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
\end{equation}
(This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  By construction, this is a flat family over $ \AA$.  We write $X_1 \ast_s X_2 $ for the scheme-theoretic fibre over a point $ s \in \AA$.

>>>>

\section{Introduction}
\label{s:intro}
% 
Throughout this paper (unless indicated otherwise) the base field is $\CC$, but it does not have to be?

@@

Let $ \Gr_{0, \CC^\times} $ denote the preimage of $\AA \setminus \{0\}$ under the map $\Gr_{0,\AA} \rightarrow \AA $.  
% 
%Composing the isomorphisms relating $\Grbd$ to $\Gr_s$ and $\Gr_s$ to $\Gr$, (\cref{it:polyno-taylor,it:grs-gr} of \cref{ss:relsbtwgrs} preceding), we obtain an isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr$.
% TODO: cf https://tex.stackexchange.com/questions/256849/cleveref-change-behaviour-of-cref-to-use-the-abbreviated-form
% 
The isomorphisms $ \tau_s $ defined above glue together to a projection map
\begin{equation}
\label{eq:mvitau}
    \tau : \Gr_{0, \CC^\times} \rightarrow \Gr \times \Gr \, .
\end{equation}
(This $\tau$ matches the map $ \tau $ of \cite{mirkovic2007geometric}, except that we are working over $ \{0 \} \times \CC^\times$ instead of the complement of the diagonal in $ \CC^2 $.)

\acom{Question for Joel: What is the benefit of working with diagonals? Letting two points vary? What is an example of a structure that you can't see letting just one point vary as we do.}

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2)$. % \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $ from \Cref{pr:grs-gr},  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \CC^\times $  of $\Grbd$.

\acom{Well you might not want but I think it would be good to tell the reader why we use the notation $\CC^\times$ for $\AA\setminus 0$ in $\AA$ or why we use the notation $\AA$ at all.. E.g.\ do we know what happens for $\GL_m(k)$ over some other base field $k$.}

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ in $ \Grbd $.  By construction, this is a flat family over $ \AA$.  We write $X_1 \ast_s X_2 $ for the scheme-theoretic fibre over a point $ s \in \AA$.
